---
title: What is Data Science?
author: Prof. Derek Sonderegger
date: Sept 14, 2020
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


## Mix of disciplines

```{r, echo=FALSE, out.height=455, out.width=800}
knitr::include_graphics(path = 'DataScience_SkillSet_v1.pdf')
```

## What is Data Science?

* Data Science is an umbrella term that encompasses skills and knowledge that are traditionally separated as Statistics and Computer Science.
* Data Science considers:
    * Acquiring data: e.g. Web Scraping, experimental design, population/sample misalignment.
    * Data Wrangling: Manipulating raw data into a usable format.
    * Data Maintenance: Data base design and storage.
    * Analysis: Inferential and predictive analyses.
    * Communication: Data reporting and visualization.



## Work Flow
```{r, echo=FALSE, out.height=455, out.width=800}
knitr::include_graphics(path = 'DataScience_Skillset_v2.pdf')
```


## Data Science is done in Context

* Almost always requires subject domain knowledge:
    * Microbiology, economics, ecology, actuarial science, finance, transportation, etc.
    
* Requires asking the *right question* and answering it with the 
*right data*.

* Because data science can mix with nearly any field, it doesn't make sense to pair with any one particular subject area.
 
    
## Lots of jobs:

* Big Tech: Amazon, IBM, Intel, Carvana, ...
* Targeted Advertising: Albertsons, Safeway, Petsmart, ...
* Financial Services: USAA, Wells Fargo, American Express, ...
* Government agencies: State of AZ Healthcare, ...
* 547 jobs in Arizona on glassdoor.com (8/19/2019)



## Required Courses - Computer Science (17 credits)

* CS 126 & 126L – Computer Science I & Lab	
* CS 136 & 136L – Computer Science II & Lab	
* CS 200 – Introduction to Computer Organization	
* CS 249 – Data Structures	
* CS 345 – Principles of Database Systems	

## Required Courses - Statistics (18 credits)

* **STA 141** – Data Visualization	
* STA 275 – Introduction to Statistical Analysis (with Calc)	
* STA 371 – Intermediate Statistics
* **STA 444, 445** - Data Wrangling
* STA 471 – Regression Analysis	
* **STA 486** - Senior Capstone (Engineering Style!)

## Other
* Math Courses
  * 136 - Calculus I
  * 226 - Discrete Mathematics
  * 216 - Matrix Algebra
* English 305W
* Electives (9 credits)
    - Essentially any upper division Math, Statistics, or Computer Science course.
    
* We encourage students to also get a minor in any field that is of interest to them.

